%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%     File: Thesis_Acknowledgments.tex                                 %
%     Tex Master: Thesis.tex                                           %
%                                                                      %
%     Author: Israel Sother                                            %
%     Last modified: 27 May 2024                                       %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{\acknowledgments}

% Add entry in the table of contents as section
\addcontentsline{toc}{section}{\acknowledgments}

First and foremost, I would like to express my gratitude to my supervisors, Prof. Sónia Pinto and Eng. Pedro Costa. I am extremely grateful to Prof. Sónia for her constant support and belief in me. She graciously accepted to supervise me under unusual academic circumstances, navigating the complexities of my double degree program with its confusing regulations. Words cannot express my gratitude to Eng. Pedro Costa, our numerous discussions went beyond academic mentoring; he not only introduced me to new concepts and directed my research but also provided crucial advice on balancing the transition out of the Formula Student life. I am deeply thankful for his technical expertise and the personal sacrifices he made to continue mentoring me.

Special thanks to Guilherme and Sergio for welcoming me to their day-to-day work in the office and for the countless hours spent discussing diverse topics.

I would like to express my heartfelt gratitude to my friends for their support throughout my work. They endured my constant focus on my research with steadfast companionship and encouragement, helping me remember the importance of setting aside time to clear my head, which was invaluable during this journey. Thanks also to Nuti and Mística for introducing me to the Formula Student world and to my group of friends from USP — Major, Comum, Y, and Soja — for all the moments together. Thank you for sharing with me some of the best years of my life.

To the FST11 and FST12 teams, your passionate dedication, tireless efforts, and countless late-night shifts were exhilarating. Together, we conquered numerous challenges and celebrated historic victories. It was an absolute pleasure to work side by side with some of the best engineers I have ever known. The memories we created together will always hold a special place in my heart and serve as a source of inspiration throughout my journey. I would like to extend my sincere thanks to a few members who became my closest friends during this period, Bruno, Duarte, Zé, Pedro, and Luis, your partnership and willingness to entertain all the crazy ideas we discussed were heartwarming, you made me feel welcome in a foreign country. Thank you all for making these years an unforgettable and extraordinary experience.

Lastly, I would be remiss in not mentioning my deepest gratitude to my family for their unwavering support and the sacrifices they made to enable me to study abroad. Choosing to pursue my education here meant greater physical distance between us, and I missed them every moment. I also want to acknowledge their understanding and patience during my Formula Student years, knowing that I dedicated far less time to them than I should have. Despite this, they supported me and embraced my passion for those cars, recognizing the lost time as an investment in something I love, and in turn, they learned to love it too. A special thank you to my sister, who consistently checked in on me and cared for my well-being, providing the much-needed boost when the days and nights of work blended into one. To my parents, thank you for being my role models and for always encouraging me to pursue my dreams wherever they led. Completing this degree is a testament to the values and education you instilled in me.

None of this would be possible without these incredible people. I am fortunate to have had their support and encouragement throughout my dissertation journey, and for that, I am deeply grateful.